### 2016-05-27 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Gas burner report: labeled instrumentation schematics, made minor edits to content

\vspace*{2\baselineskip}
February 2016}}

@@

Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor. Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor. The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door.
\clearpage

@@

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2\%~\cite{Romet:2014}. The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm13$\%. ***\textit{Still need to finish uncertainty estimate and include refs}***

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests 2--6, were conducted in the East Structure. Table~\ref{table:HRR_East} lists the calculated heat release rate for each test.

Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. During Tests~2--4, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. During all other experiments, however, the south exterior doorway was not used to change the ventilation pattern of the structure and thus remained closed for the entirety of the test. For these tests, the hinged door was removed and gypsum board was used to fully close the doorway. A 533~mm (21~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the doorway and used during Tests~2--4.

The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved performing a specific set of events three times sequentially. To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables).

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 901 & 634 & 330 \\
Test 3 				& 326 & 650	& 905 & 631 & 326 \\
Test 4				& 351 & 654	& 952 & 652 & 337 \\
\midrule
 & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
& \multicolumn{3}{c}{} \\
\midrule
Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	21:00		  &		4:00		&		4:00	  \\
	~(2)~ Middle burner on 				&   24:00		  &		7:00		&		7:00	  \\
	~(3)~ Center burner on 				&   27:00		  &	   10:00		&	   10:00	  \\
	~(4)~ West double door opened 		&   28:00		  &    11:00		&	   11:00	  \\
	~(5)~ East double door opened 		&   30:00		  &    13:00		&	   13:00	  \\
	~(6)~ South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
	~(7)~ Center burner off				&   33:00		  &    17:00		&	   17:00	  \\
	~(8)~ Middle burner off				&   35:00		  &    19:00		&	   19:00	  \\
	~(9)~ Corner burner off				&   37:00		  &    21:00		&	   21:00	  \\
	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
	(11) PPV fan off 					& 	52:30 		  &    36:00  		&  	   36:00$^*$  \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	~(1)~ All burners on 			& 	14:30		  &	   35:00		&	   55:00	\\
	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
	~(1)~ All burners on 			&	3:45	&	13:15	&	21:45	\\
	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

\section{West Structure Tests}
\label{sec:west_procedure}
Four different tests, Tests~22--25, were conducted in the West Structure. Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 533~mm (21~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure. During Tests~22 and 23, the fan was aimed at the center of the double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& All burners on \\
 \midrule
Test 22				&     	764 	  \\
Test 23				&     	789 	  \\
Test 24				& 	    789 	  \\
Test 25				&     	786 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

>>>>

\vspace*{2\baselineskip}
May 2016}}

@@

Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor. Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor. The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door. The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:west_channel_list}.
% \clearpage

@@

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2\%~\cite{Romet:2014}. The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm??$\%. ***\textit{Still need to finish reviewing literature about HRR uncertainty and add description here about calculation and uncertainty estimate.}***

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests 2--6, were conducted in the East Structure.  Table~\ref{table:HRR_East} lists the heat release rates for each experiment. The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds. Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.

Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. A 533~mm (21~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4. During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test. To fully close the doorway during these tests, the hinged door was removed and gypsum board was used to cover the doorway.

The procedures for Test~5 and Test~6 are outlined in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved repeating a specific set of events three times in a row. To avoid listing the identical actions three separate times in the event column of the table, each repetition of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables) and given its own column in the event table.

\begin{table}[!ht]
\caption{Heat Release Rates for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 901 & 634 & 330 \\
Test 3 				& 326 & 650	& 905 & 631 & 326 \\
Test 4				& 351 & 654	& 952 & 652 & 337 \\
\midrule
 & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
& \multicolumn{3}{c}{} \\
\midrule
Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	21:00		  &		4:00		&		4:00	  \\
	~(2)~ Middle burner on 				&   24:00		  &		7:00		&		7:00	  \\
	~(3)~ Center burner on 				&   27:00		  &	   10:00		&	   10:00	  \\
	~(4)~ West double door opened 		&   28:00		  &    11:00		&	   11:00	  \\
	~(5)~ East double door opened 		&   30:00		  &    13:00		&	   13:00	  \\
	~(6)~ South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
	~(7)~ Center burner off				&   33:00		  &    17:00		&	   17:00	  \\
	~(8)~ Middle burner off				&   35:00		  &    19:00		&	   19:00	  \\
	~(9)~ Corner burner off				&   37:00		  &    21:00		&	   21:00	  \\
	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
	(11) PPV fan off 					& 	52:30 		  &    N/A  		&  	   N/A        \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	~(1)~ All burners on 			& 	14:00		  &	   34:30		&	   54:30	\\
	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
	~(1)~ All burners on 			&	3:15	&	12:45	&	21:45	\\
	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

\section{West Structure Tests}
\label{sec:west_procedure}
Four different tests, Tests~22--25, were conducted in the West Structure. Table~\ref{table:HRR_West} lists the calculated heat release rate for each test. Similar to Tests~5 and 6, Tests~22--25 had a duration on the order of seconds between the ignition of each burner, so only the heat release rate for when all three burners were ignited is reported.

\begin{table}[!ht]
\caption{Heat Release Rates for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& All burners on \\
 \midrule
Test 22				&     	764 	  \\
Test 23				&     	789 	  \\
Test 24				& 	    789 	  \\
Test 25				&     	786 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 533~mm (21~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure. During Tests~22 and 23, the fan was aimed at the center of both double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.
